### 2019-02-24 implementation.tex
simple example

>>>>

\begin{figure}
\begin{code}
@import random
\vspace{0.1in}
<@
storage = []
\vspace{0.1in}
def init():
    global storage
    storage = []
\vspace{0.1in}
def store(n):
    global storage
    if n in storage:
       raise KeyError
    storage.append(n)
    if n < 0:
       raise ValueError
@>
\vspace{0.1in}
init: init()
\vspace{0.1in}
pool: <int> 5
\vspace{0.1in}
<int> := <[-10..10]>
<int> := random.randint(-100,100)
{KeyError,ValueError} store(<int>)
\end{code}
\caption{A trivial example containing (independent) vertical and
  horizonal nondeterminisms}
\label{fig:simpleexample}
\end{figure}

Figure \ref{fig:simpleexample} shows a self-contained example of a
Python program and test harness with both vertical and horizontal nondeterminism.
